\documentclass[a4paper,10pt]{article}

\newif\ifpdf
\ifx\pdfoutput\undefined
\pdffalse
\else
\pdfoutput=1
\pdftrue
\fi

\ifpdf
\usepackage{color}
\definecolor{black}{rgb}{0,0,0}
\usepackage[
	pdftex,
	colorlinks=true,
	urlcolor=black,
	filecolor=black,
	linkcolor=black,
	pdftitle={Description of the scary protocol},
	pdfauthor={Christoph Frick <rid@zefix.tv>},
	pagebackref,
	pdfpagemode=UseOutlines,
	bookmarksopen=true]{hyperref}
\pdfcompresslevel=3
\fi

\newcommand{\scary}{{\it scary}}
\newcommand{\rls}{{\it Race List Server}}
\newcommand{\rlc}{{\it Race List Client}}
\newcommand{\gplop}{{\it iGOR}}
\newcommand{\gplopdev}{{\it iGOR Development Group}}

\newcommand{\scaryport}{31997}


\begin{document}

\title{Description of the \scary\ protocol}
\author{Phil Flack, Christoph Frick}

\maketitle

\vspace{2in}

\abstract

The \scary protocol is used between any \rlc\ and any \rls\ as middleware for
sending requests to the server adding, updating, querying and deleting
informations. This document describes the protocol itself and the commands
used over it.\\

The \scary\ protocol may only be used by applications, that are allowed to use
it. This is valid both for \rlc's and \rls's. The use without the written
permission of the \gplopdev is strictly forbidden.\\

Copyright (c) 2002-2004 Phil Flack
          
Copyright (c) 2002-2004 Christoph Frick
          
Copyright (c) 2002-2004 \gplopdev

All rights reserved

\newpage


\section{Protocol}

The protocol itself uses TCP/IP for connections between the \rlc\ (client) and
the \rls\ (server). The client connects to the server on the default port
(\scaryport). The client send the {\it request} to the server. The server then
forges a {\it reply} to the request and sends it back to the client. The
server then ends the connections. Only one request/reply per connection is
sent.\\

The data representing the request or the reply are wrapped in the following
fashion:\\

{\tt IIIICSSSS}\\

\begin{description}

\item {\tt IIII}\\
This is the ident string for this protocol. The ident are the chars: {\tt w196} \\

\item {\tt C}\\
This flag defines whether the data are gnuzip compressed data or clear text.
For compressed data a {\tt C} is used - and for clear text a {\tt T}

\item {\tt SSSS}\\
This is the size of the request, the other side has to expect to read then.
The number is an {\it unsigned long int} in {\it network byte order}.  The
size of the data transmitted is always the real size to read from the socket.

\end{description}

If the data are compressed the next four bytes are the size of the data after
the compression. This number does count for the {\tt SSSS} size and its stored
like this number as {\it unsigned long int} in {\it network byte order}.\\

After the interpretation of the header, the given amount of bytes is read from
the socket. The data are encoded in ISO-8859-1.\\

To allow a common way to separate the different fields in the data the
following scheme is used to establish a table like handling of the data. The
char {\tt $\backslash$002} is used to separate {\bf lines}. The char {\tt
$\backslash$001} is used to separate {\bf cells/columns}.\\

No string informations of the programming language, which is used for the
implementation, are sent to the other side (e.g. $\backslash$000 chars in
C).\\

Within the data the command is always the the first cell. After the command
all the parameters to the command are the following cells in this line. The
parameters are in a fixed order. Also there are serverside checks for each
parameter.\\

The reply of the server contains in the first line the status of the reply.
The first line contains two cells. The first is a number, that stands for a
group of errors. The second cell contains a message, that gives an accurate
description for the number. The following numbers are used:\\

\begin{description}

\item 200 \\
The request is fine - expect the data -- if there is some additional reply --
to be found in the following rows. The reply depends on the command. The
replies are described in the next section.

\item 400 \\
There is an error with the request. See the description for details. Most
common are errors with the amount or the type of the submitted parameters.

\item 401 \\
The execution of this command needs a valid client id. Either the user is not
logged in or the user has been dropped due to inactivity for a long period.

\item 404 \\
The resource used in the request is not (longer) known. This is most common,
when sending server ids and the server is already dropped from the list due to
longer inactivity.

\item 500 \\
There is an internal server error. This should not happen, so it would be good
to have here a useful description about which command resulted in this error
and if possible how to reproduce this error. Inform the developer of the
server about this issue or the administrator of the server and try to provide
him with as many informations as possible.

\item 501 \\
The command is not yet implemented. If your client application depends on this
command, get in contact with the developer or the administrator of the server.

\end{description}

% this part is generated from the server
\include{command_documentation}

\end{document}
